---
title: "VivekArora_RegressionAnalysis"
output: word_document
date: "2024-10-19"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
mortgage_data <- read.csv("Case Study Part VI Mortgage Repayment Dataset.csv")
# Install necessary libraries (only needs to be done once)
if (!require(pscl)) install.packages('pscl', dependencies=TRUE)
# Load necessary libraries
library(pscl)

# Step 2: Data Cleaning and Imputation

# Convert loan_status to a factor (1 for Fully Paid, 0 for Charged Off)
mortgage_data$loan_status <- ifelse(mortgage_data$loan_status == "Fully Paid", 1, 0)

# Clean 'term' to keep only the numeric value
mortgage_data$term <- as.numeric(gsub(" months", "", mortgage_data$term))

# Clean 'int_rate' to remove '%' and convert to numeric
mortgage_data$int_rate <- as.numeric(gsub("%", "", mortgage_data$int_rate))

# Convert 'emp_length' to numeric
mortgage_data$emp_length <- gsub("10\\+ years", "10", mortgage_data$emp_length)
mortgage_data$emp_length <- gsub("< 1 year", "0", mortgage_data$emp_length)
mortgage_data$emp_length <- gsub(" years", "", mortgage_data$emp_length)
mortgage_data$emp_length <- gsub(" year", "", mortgage_data$emp_length)
mortgage_data$emp_length <- as.numeric(mortgage_data$emp_length)

# Replace NA values with the mean for numeric columns

# Impute mean for financial variables
numeric_columns_mean <- c("loan_amnt", "term", "int_rate", "annual_inc", "dti")

for (col in numeric_columns_mean) {
  mortgage_data[[col]][is.na(mortgage_data[[col]])] <- mean(mortgage_data[[col]], na.rm = TRUE)
}

# Impute 0 for employment length
mortgage_data$emp_length[is.na(mortgage_data$emp_length)] <- 0

# Step 3: Build the Logistic Regression Model

# Build the logistic regression model
model <- glm(loan_status ~ loan_amnt + term + int_rate + emp_length + annual_inc + dti,
             family = binomial(link = 'logit'), data = mortgage_data)

# View the summary of the model
summary(model)

# Step 4: Evaluate the Model

# Calculate McFadden's R-squared value
pR2(model)

